Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-12-17 paper/tex/appendix.tex
switch to pdf figs

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/NZsumplot_12codes_scottsrule.jpg}
\caption{The smoothed stacked estimator $\hat{N}(z)$ of the redshift distribution (red) produced by each code (panels) compared to the true redshift distribution $\tilde{N}(z)$ (blue).
Varying levels of agreement are seen among the codes, with the smallest deviations for \cmnn, \flexzboost, \tpz, and \trainz.}
\label{fig:nz}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_NZ_withnull_jpg.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the $\hat{N}(z)$ distributions.
Horizontal lines indicate the statistic values (including uncertainty) achieved using \trainz\ via bootstrap resampling a training set containing 30,000 redshifts.
We make the reassuring observation that these related statistics do not disagree significantly with one another.
\cmnn\ outperforms the control case, \trainz, and several codes are within a factor of two of this conservative idealized limit.
\skynet\ scores poorly due to an overall bias in its redshift predictions.}
\label{fig:nz_stats}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.75\textwidth]{fig/momentsplot_10yr.jpg}
\caption{Residuals of the first three moments of the stacked $\hat{N}(z)$ distribution.  Red and blue horizontal lines indicate the Year 10 DESC SRD requirements on accuracy of the mean and variance respectively.  Only a small number of codes are able to meet these specifications even with perfect training data.   }
\label{fig:moments}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.49\textwidth]{fig/ZPEAK_szpz_threecolumn_12codes_navy_lowalpha.jpg}
\includegraphics[width=0.49\textwidth]{fig/ZWEIGHT_szpz_threecolumn_12codes_navy_lowalpha.jpg}
\caption{The density of \pz\ point estimates (contours) reduced from the \pzpdf s with outliers (blue) beyond the outlier cutoff (red dashed lines), via the mode ($z_{PEAK}$, left panel) and main-peak-mean ($z_{WEIGHT}$, right panel).
The \trainz\ estimator (lower right sub-panels) has a shared $z_{PEAK}$ and $z_{WEIGHT}$ for the entire test set galaxy sample.}
\label{fig:pz_pointestimates}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/NZsumplot_12codes_scottsrule.pdf}
\caption{The smoothed stacked estimator $\hat{N}(z)$ of the redshift distribution (red) produced by each code (panels) compared to the true redshift distribution $\tilde{N}(z)$ (blue).
Varying levels of agreement are seen among the codes, with the smallest deviations for \cmnn, \flexzboost, \tpz, and \trainz.}
\label{fig:nz}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_NZ_withnull_jpg.pdf}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the $\hat{N}(z)$ distributions.
Horizontal lines indicate the statistic values (including uncertainty) achieved using \trainz\ via bootstrap resampling a training set containing 30,000 redshifts.
We make the reassuring observation that these related statistics do not disagree significantly with one another.
\cmnn\ outperforms the control case, \trainz, and several codes are within a factor of two of this conservative idealized limit.
\skynet\ scores poorly due to an overall bias in its redshift predictions.}
\label{fig:nz_stats}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.75\textwidth]{fig/momentsplot_10yr.pdf}
\caption{Residuals of the first three moments of the stacked $\hat{N}(z)$ distribution.  Red and blue horizontal lines indicate the Year 10 DESC SRD requirements on accuracy of the mean and variance respectively.  Only a small number of codes are able to meet these specifications even with perfect training data.   }
\label{fig:moments}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.49\textwidth]{fig/ZPEAK_szpz_threecolumn_12codes_navy_lowalpha.pdf}
\includegraphics[width=0.49\textwidth]{fig/ZWEIGHT_szpz_threecolumn_12codes_navy_lowalpha.pdf}
\caption{The density of \pz\ point estimates (contours) reduced from the \pzpdf s with outliers (blue) beyond the outlier cutoff (red dashed lines), via the mode ($z_{PEAK}$, left panel) and main-peak-mean ($z_{WEIGHT}$, right panel).
The \trainz\ estimator (lower right sub-panels) has a shared $z_{PEAK}$ and $z_{WEIGHT}$ for the entire test set galaxy sample.}
\label{fig:pz_pointestimates}
\end{figure*}

### 2019-12-17 paper/tex/results.tex
switch to pdf figs

\section{Results}
\label{sec:results}
%(Sam Schmidt, Bryce Kalmbach, Johann Cohen Tanugi, Rongpu Zhou, Alex Malz)

@@

\begin{figure*}
%\centering
\includegraphics[width=0.49\textwidth]{fig/pz_12codes_261931_noseaborn_crop.jpg}\includegraphics[width=0.49\textwidth]{fig/pz_12codes_471167_noseaborn_crop.jpg}\\
\includegraphics[width=0.49\textwidth]{fig/pz_12codes_713178_noseaborn_crop.jpg}\includegraphics[width=0.49\textwidth]{fig/pz_12codes_982747_noseaborn_crop.jpg}
\caption{The individual \pzpdf s (blue) distributions produced by the twelve codes (small panels) on four exemplary galaxies' photometry (large panels) with different true redshifts (red).
All \pzpdf s have been scaled to the same peak value.
The \pzpdf s of all codes share some features for the example galaxies due to physical colour degeneracies and photometric errors: tight unimodal $p(z)$ (upper left), broad unimodal $p(z)$ (upper right), bimodal $p(z)$ (lower right), and complex/multimodal $p(z)$ (lower left).
The diverse algorithms and implementations induce differences in small-scale structure and sensitivity to physical systematics.}
\label{fig:pz_examples}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/PITANDQQplot_12codes_withsigmaband_crop.jpg}
\caption{The QQ plot (red) and PIT histogram (blue) of the \pzpdf\ codes (panels) along with the ideal QQ (black dashed diagonal) and ideal PIT (gray horizontal) curves, as well as a difference plot for the QQ difference from the ideal diagonal (lower inset).
The gray shaded region indicates the $2 \sigma$ range from a bootstrap resampling of the training set with a size of 30,000 galaxies using \trainz.
The twelve codes exhibit varying degrees of four deviations from perfection: an overabundance of PIT values at the centre of the distribution indicate a catalogue of overly broad \pzpdf s, an excess of PIT values at the extrema indicates a catalogue of overly narrow \pzpdf s, catastrophic outliers manifest as overabundances at PIT values of 0 and 1, and asymmetry indicates systematic bias, a form of model misspecification.
Values in excess of the $2\sigma$ shaded region show that for some codes these errors will be significant given expected training sample sizes.}
\label{fig:pitqq}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_PIT_withnull_jpg.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the PIT distributions.
There is generally good agreement between these statistics, with differences corresponding to the codes with outstanding catastrophic outlier rates, a reflection of the differences in how each statistic weights the tails of the distribution.
Horizontal lines indicate the level of uncertainty found by bootstrapping a training set sample of 30,000 galaxies using \trainz; none of the codes reach this conservative ideal floor in expected uncertainty.}
\label{fig:pit_stats}
\end{figure*}

@@

\begin{table}  %%% DATA TABLE %%%
\centering
\caption{CDE loss statistic of the individual \pzpdf s for each code.
A lower value of the CDE loss indicates more accurate individual \pzpdf s, with \cmnn\ and \flexzboost\ performing best under this metric.}
\label{tab:cdeloss}
\begin{tabular}{lr}
\hline
Photo-$z$ Code & CDE Loss \\
\hline
\annz 	    & $-6.88$ \\
\bpz 		    & $-7.82$ \\
%\textsc{Delight} 	& $-4.06$ \\
\delight    & $-8.33$\\
%\textsc{EAZY} 		& $-7.97$ \\
\eazy       & $-7.07$ \\
%\textsc{FlexZBoost} & $-11.51$ \\
\flexzboost & $-10.60$\\
\gpz		    & $-9.93$ \\
\lephare 	  & $-1.66$ \\
\metaphor 	& $-6.28$ \\
%\textsc{CMNN} 		& $-$ \\
\cmnn       & $-10.43$ \\
\skynet 	  & $-7.89$ \\
\tpz 		    & $-9.55$ \\
\hline
\trainz		  & $-0.83$ \\
%\textsc{Frankenz}	& $-$  \\
%\hline
\end{tabular}
\end{table}

>>>>

\section{Results}
\label{sec:results}

@@

\begin{figure*}
%\centering
\includegraphics[width=0.49\textwidth]{fig/pz_12codes_261931_noseaborn_crop.pdf}\includegraphics[width=0.49\textwidth]{fig/pz_12codes_471167_noseaborn_crop.pdf}\\
\includegraphics[width=0.49\textwidth]{fig/pz_12codes_713178_noseaborn_crop.pdf}\includegraphics[width=0.49\textwidth]{fig/pz_12codes_982747_noseaborn_crop.pdf}
\caption{The individual \pzpdf s (blue) distributions produced by the twelve codes (small panels) on four exemplary galaxies' photometry (large panels) with different true redshifts (red).
All \pzpdf s have been scaled to the same peak value.
The \pzpdf s of all codes share some features for the example galaxies due to physical colour degeneracies and photometric errors: tight unimodal $p(z)$ (upper left), broad unimodal $p(z)$ (upper right), bimodal $p(z)$ (lower right), and complex/multimodal $p(z)$ (lower left).
The diverse algorithms and implementations induce differences in small-scale structure and sensitivity to physical systematics.}
\label{fig:pz_examples}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/PITANDQQplot_12codes_withsigmaband_crop.pdf}
\caption{The QQ plot (red) and PIT histogram (blue) of the \pzpdf\ codes (panels) along with the ideal QQ (black dashed diagonal) and ideal PIT (gray horizontal) curves, as well as a difference plot for the QQ difference from the ideal diagonal (lower inset).
The gray shaded region indicates the $2 \sigma$ range from a bootstrap resampling of the training set with a size of 30,000 galaxies using \trainz.
The twelve codes exhibit varying degrees of four deviations from perfection: an overabundance of PIT values at the centre of the distribution indicate a catalogue of overly broad \pzpdf s, an excess of PIT values at the extrema indicates a catalogue of overly narrow \pzpdf s, catastrophic outliers manifest as overabundances at PIT values of 0 and 1, and asymmetry indicates systematic bias, a form of model misspecification.
Values in excess of the $2\sigma$ shaded region show that for some codes these errors will be significant given expected training sample sizes.}
\label{fig:pitqq}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_PIT_withnull_jpg.pdf}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the PIT distributions.
There is generally good agreement between these statistics, with differences corresponding to the codes with outstanding catastrophic outlier rates, a reflection of the differences in how each statistic weights the tails of the distribution.
Horizontal lines indicate the level of uncertainty found by bootstrapping a training set sample of 30,000 galaxies using \trainz; none of the codes reach this conservative ideal floor in expected uncertainty.}
\label{fig:pit_stats}
\end{figure*}

@@

\begin{table}  %%% DATA TABLE %%%
\centering
\caption{CDE loss statistic of the individual \pzpdf s for each code.
A lower value of the CDE loss indicates more accurate individual \pzpdf s, with \cmnn\ and \flexzboost\ performing best under this metric.}
\label{tab:cdeloss}
\begin{tabular}{lr}
\hline
Photo-$z$ Code & CDE Loss \\
\hline
\annz 	    & $-6.88$ \\
\bpz 		    & $-7.82$ \\
\delight    & $-8.33$\\
\eazy       & $-7.07$ \\
\flexzboost & $-10.60$\\
\gpz		    & $-9.93$ \\
\lephare 	  & $-1.66$ \\
\metaphor 	& $-6.28$ \\
\cmnn       & $-10.43$ \\
\skynet 	  & $-7.89$ \\
\tpz 		    & $-9.55$ \\
\hline
\trainz		  & $-0.83$ \\
\end{tabular}
\end{table}
